---
title: "Clustering_VasanthakumarKalaikkovan"
author: "Vasanthakumar Kalaikkovan"
date: "29/05/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Clustering

In this problem, you will use the k-means clustering algorithm to look for patterns in an unlabeled dataset. The dataset for this problem is found at data/clustering-data.csv.

```{r library importing and data importing}
library(stats)
library(ggplot2)

getwd()

setwd("E://Repos/StatisticsR/DSC520-Statistics/week11")

cluster_df <- read.csv("clustering-data.csv")
```

Plot the dataset using a scatter plot.

```{r Scatter Plots}
ggplot(cluster_df,aes(x=x,y=y))+geom_point()+labs(title="Clustering Scatter Plot")
```
Fit the dataset using the k-means algorithm from k=2 to k=12. Create a scatter plot of the resultant clusters for each value of k.

```{r Clustter Scatter plot}
set.seed(2345)
clusters <-NULL
avg_dist <- NULL

for(i in 2:12)
{
  clusters_kMeans <- kmeans(cluster_df,i)
  clusters[i] <- as.data.frame(clusters_kMeans[["cluster"]])
  cluster_df["cluster"] <- clusters[i]
  
  avg_dist[i] <- sum(clusters_kMeans[["withinss"]]/clusters_kMeans[["size"]])
  
  print(ggplot(cluster_df,aes(x=x,y=y,color=as.factor(cluster)))+geom_point()+labs(title = "Cluster Scatterplot"))
  print(avg_dist[i])
}
```
Calculate this average distance from the center of each cluster for each value of k and plot it as a line chart where k is the x-axis and the average distance is the y-axis.
One way of determining the “right” number of clusters is to look at the graph of k versus average distance and finding the “elbow point”. Looking at the graph you generated in the previous example, what is the elbow point for this dataset?

```{r avg. distance values}
plot(2:12,avg_dist[2:12],main="Average Euclidian Distance for k=2:12")
```

Elbow, k=9






















