---
title: "ASSIGNMENT 4"
author: "Vasanthakumar Kalaikkovan"
date: '2021-04-21'
output:
  pdf_document: default
  html_document: default
  word_document: default
bibliography: bibliography.bib
---

# Markdown Basics

## Favorite Foods

1. Briyani
2. Pizza
3. Burger

## Images

image: ![](E:/Repos/StatisticsR/DSC520-Statistics/assignment04/All Cases (Log Plot)/10-all-cases-log.png) 

## Add a Quote

>It is very easy to defeat someone, but very difficult to win someone

## Add an Equation

$A = \pi*r^{2}$ 

## Add a Footnote

This is a footnote

## Add Citations

* R for Everyone
* Discovering Statistics Using R

# Inline Code

```{r include=TRUE}
library(ggplot2)
theme_set(theme_minimal())
covid_df <- read.csv("E:/Repos/StatisticsR/DSC520-Statistics/data/nytimes/covid-19-data/us-states.csv")
heights_df <- read.csv("E:/Repos/StatisticsR/DSC520-Statistics/data/r4ds/heights.csv")
ggplot(heights_df, aes(x=sex, y=earn)) + geom_point()+ geom_boxplot()

covid_df <- read.csv("E:/Repos/StatisticsR/DSC520-Statistics/data/nytimes/covid-19-data/us-states.csv")
covid_df$date <- as.Date(covid_df$date)
california_df <- covid_df[ which( covid_df$state == "California"), ]
ny_df <- covid_df[ which( covid_df$state == "New York"), ]
florida_df <- covid_df[ which( covid_df$state == "Florida"), ]
```

## NY Times COVID-19 Data
```{r echo=FALSE}
ggplot(data=florida_df, aes(x=date, group=1)) +
  geom_line(aes(y = cases, colour = "Florida")) +
  geom_line(data=ny_df, aes(y = cases,colour="New York")) +
  geom_line(data=california_df, aes(y = cases, colour="California")) +
  scale_colour_manual("",
                      breaks = c("Florida", "New York", "California"),
                      values = c("darkred", "darkgreen", "steelblue")) +
  xlab(" ") + ylab("Cases") + scale_y_log10()

```

## R4DS Height vs Earnings
```{r echo=FALSE}
ggplot(heights_df, aes(x=race, y=earn)) + geom_point()+ geom_boxplot()
```

# Tables

## Knitr Table with Kable
```{r include=TRUE}
names<-c("Aragon","Bilbo","Frodo","Sam","Sauron")
race<-c("Men","Hobbit","Hobbit","Hobbit","Maia")
fellow<-c("Yes","No","Yes","Yes","No")
ring<-c("No","Yes","Yes","Yes","Yes")
age<-c("88","129","51","36","7052")
lord_of_ring<-cbind(names,race,fellow,ring,age)
colnames(lord_of_ring)<-c("Name","Race","In Fellowship?","Is Ring Bearer?","Age")
knitr::kable(lord_of_ring, "pipe",caption="One Ring to Rule Them All")
```

## Pandoc Table
pandoc.table(lord_of_ring, style = 'grid')

# References

